Detecting AI-Generated Images using ResNet

### 2022-12-12 paper/paper.tex
Update paper structure
Update paper
Update Paper
WIP paper datasets section

\title{Detecting AI-Generated Images}

@@

Datasets go here.

@@

>>>>

\title{Detecting AI-Generated Images  using ResNet}

@@

In order to train a classifier that can distinguish between real and generated images, we need a labeled dataset that consists both of real and generated images for supervised learning. Datasets of this kind is not common, and we'd like to experiment on the latest state-of-the-art image generation AI models, such as DALL·E 2 and Stable Diffusion. We started with real photos from existing public datasets as our raw datasets. Then, we use Diffusers-based image-to-image model to generate images from real photos. This way, we ended up with a labeled dataset of real photos and generated photos.

\subsection{Raw Datasets}

\subsection{Diffusers}

\subsubsection{CLIP guidance}

\subsubsection{Stable Diffusion}

\subsubsection{DALL·E 2}

@@

\subsection{Experiment Settings}

Experiment Settings go here.
